\vspace{-2cm} Government websites as data: A methodological pipeline with application to the websites of municipalities in the United States

### 2018-08-10 paper/manuscript.tex
fixed the same issue for table 7 and removed the last few @markus from the manuscript

We rely on a random forest as the final classifier, which offers slightly better performance than logistic regression.\footnote{We also tried SVM, boosted trees and AdaBoost, with similar results and chose the random forests because this method has a probabilistic basis and is more intuitive.} We assess performance of this classifier through five-fold cross-validation. This means that the classifier is trained on 400 samples and then tested on the held-out set of 100, measuring metrics such as percent correctly predicted, precision, recall, and F1 score. This procedure is carried out five times, so that each sample is part of the test set once. The aggregated (mean) results of this process can be found in Table \ref{randomForest}. For the implementation of this method, we rely on the R package \texttt{caret}, whose random forest classifier is based on the package \texttt{ranger}. We use this classifier to flag and remove all lines that are not classified (based on a threshold of $p = 0.5$) as substantively meaningful. The effect of this process on the corpus is illustrated with the corpus of Anchorage, AK (i.e. a city that isn't part of our sample used in the analysis) as an example in Figures \ref{boilerplate_before_after1} to \ref{boilerplate_before_after4}. Before the lines identified by the classifier as boilerplate are removed, lines with very few characters and words are the most common. After the removal, the distribution has changed---lines of medium length now occur more frequently than extremely short ones, which are unlikely to be substantively meaningful (see figures \ref{boilerplate_before_after1} and \ref{boilerplate_before_after2}). Furthermore, lines that are duplicated only a few times rather than dozens, hundreds or even thousands are now more common (see figure \ref{boilerplate_before_after3}). Finally, the position of the line within the documents is not as important to the random forest, and this also shows in the results. However, this feature still has a positive effect, as lines at either end of the document are a bit less common now (see figure \ref{boilerplate_before_after4}). [@markus, this is an excellent demonstration of the effect of the classifier. When you get a chance, would you also add a table listing the top 10 most likely boilerplate lines---to provide face validity that we are accurately flagging boilerplate?] After all the preprocessing is set and done, our corpus consists of 259,099 documents.

@@

The structural topic model is implemented in the R package \texttt{STM} \citep{stm}. We use 60 topics---the number recommended by the authors [@markus, please add a cite to the specific document in which this number is suggested?] for medium- to large-sized corpora. Since our corpus is at the larger end of that spectrum, the appendix also contains the results of a model with 120 topics, which corroborates the findings of the one presented here. We use four covariates: First, \textit{party}, to estimate the difference in topic prevalence based on whether mayors are Republican or Democratic. Second, \textit{city population}, which the literature frequently emphasizes as a determinant of the issues a city faces (see, for example, \cite{Guillamon2013}). Third, we control for wealth by relying on \textit{median income} as a covariate, which we use as a proxy for the tax base in a city. Fourth and finally, we include state dummy variables, which should account for language that is associated with state-specific issues, and general background variables that vary across states.

@@

The results are shown in table \ref{tabSTMtopwords60}. The rows of the table are sorted so that the most Republican topics (marked by a deeper red color) appear at the top, and the most Democratic ones (blue) at the bottom. The degree of partisanship shown in the table is determined by the size and direction of the coefficient of the party variable for each topic. The topics that are entirely white have 90\% credible intervals on the effect of mayoral party that include zero.  [@markus, do the results from the stm package allow us to say anything about whether the overall fit of the model improved from adding party? if so, can we mention that?].

@@

%US map
\begin{figure}[htp]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Cities in the corpus, by partisanship of mayor. \textbf{REVISE to remove everything not in our six states.}}
	\label{us_map}
	\includegraphics[width=\linewidth]{figures/us_map.pdf}
\end{figure}

>>>>

We rely on a random forest as the final classifier, which offers slightly better performance than logistic regression.\footnote{We also tried SVM, boosted trees and AdaBoost, with similar results and chose the random forests because this method has a probabilistic basis and is more intuitive.} We assess performance of this classifier through five-fold cross-validation. This means that the classifier is trained on 400 samples and then tested on the held-out set of 100, measuring metrics such as percent correctly predicted, precision, recall, and F1 score. This procedure is carried out five times, so that each sample is part of the test set once. The aggregated (mean) results of this process can be found in Table \ref{randomForest}. For the implementation of this method, we rely on the R package \texttt{caret}, whose random forest classifier is based on the package \texttt{ranger}. We use this classifier to flag and remove all lines that are not classified (based on a threshold of $p = 0.5$) as substantively meaningful. The effect of this process on the corpus is illustrated with the corpus of Anchorage, AK (i.e. a city that isn't part of our sample used in the analysis) as an example in Figures \ref{boilerplate_before_after1} to \ref{boilerplate_before_after4}. Before the lines identified by the classifier as boilerplate are removed, lines with very few characters and words are the most common. After the removal, the distribution has changed---lines of medium length now occur more frequently than extremely short ones, which are unlikely to be substantively meaningful (see figures \ref{boilerplate_before_after1} and \ref{boilerplate_before_after2}). Furthermore, lines that are duplicated only a few times rather than dozens, hundreds or even thousands are now more common (see figure \ref{boilerplate_before_after3}). Finally, the position of the line within the documents is not as important to the random forest, and this also shows in the results. However, this feature still has a positive effect, as lines at either end of the document are a bit less common now (see figure \ref{boilerplate_before_after4}). Table \ref{tabBoilerplateIllustration} provides further illustration by listing the top 10 most likely boilerplate lines (in Anchorage, AK) -- all of which were flagged as such with a probability of 1. After all the preprocessing is set and done, our corpus consists of 259,099 documents.

@@

The structural topic model is implemented in the R package \texttt{STM} \citep{stm}. We use 60 topics---the number recommended by the authors\footnote{For this recommendation, see the documentation for the function \texttt{stm()} in version 1.3.0 of the R package \texttt{stm} \citep{stm}.} for medium- to large-sized corpora. Since our corpus is at the larger end of that spectrum, the appendix also contains the results of a model with 120 topics, which corroborates the findings of the one presented here. We use four covariates: First, \textit{party}, to estimate the difference in topic prevalence based on whether mayors are Republican or Democratic. Second, \textit{city population}, which the literature frequently emphasizes as a determinant of the issues a city faces (see, for example, \cite{Guillamon2013}). Third, we control for wealth by relying on \textit{median income} as a covariate, which we use as a proxy for the tax base in a city. Fourth and finally, we include state dummy variables, which should account for language that is associated with state-specific issues, and general background variables that vary across states.

@@

The results are shown in Table \ref{tabSTMtopwords60}. The rows of the table are sorted so that the most Republican topics (marked by a deeper red color) appear at the top, and the most Democratic ones (blue) at the bottom. The degree of partisanship shown in the table is determined by the size and direction of the coefficient of the party variable for each topic. The topics that are entirely white have 90\% credible intervals on the effect of mayoral party that include zero.

@@

%US map
\begin{figure}[htp]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Cities in the corpus, by partisanship of mayor.}
	\label{us_map}
	\includegraphics[width=\linewidth]{figures/us_map.pdf}
\end{figure}
